\documentclass{article}

% \topmargin=-0.5in
% \oddsidemargin=0in
% \evensidemargin=0in
% \textwidth=6.5in
% \textheight=9.0in

%% \title{CS131: Programming Languages \\
%%   Academic Honesty Policy}

%% \date{January 9, 2006}

\begin{document}
%% \advance\baselineskip by0.5pt

%% \maketitle

\begin{large}
\begin{center}
CS97 Academic Honesty Policy\\
Fall 2017
\end{center}
\end{large}

\begin{enumerate}
\item 
Unless stated otherwise, each student must turn in his/her
own homework assignment.  The code in this assignment must be your
code; the words must be your words.  One consequence of this rule:
{\bf If you cannot explain your assignment to me (why you did it the
  way you did, how it works, etc.), then you have violated our policy.}

\item You can learn a lot from others in the class, and other people
  in general, and I encourage
you to do so.  Therefore, you are allowed to talk to others about the course content.  You may also talk to others about
assignments, but {\bf you should never see another student's answers and
  you should never show your answers to anyone else or post your code in a public place}, such as Piazza or Github, either now or in the future.

Further, you must
list the people with whom you interact at the top of your assignment.  One consequence of this rule:
You cannot violate the policy by listing names, only by omitting names.

\item You are also allowed to use resources such as books or the Web.
Again, you must simply list these resources at the top of your
assignment.  However, {\bf you may not search for solutions to the homework problems}.
\end{enumerate}

The policy is enforced by both manual and automated analysis of your
homework submissions.  {\bf All policy violations are reported to the Dean},
who does a full
investigation and determines appropriate punishment.  

% In order to have any work graded, you must sign and return this form.

\medskip
\textbf{I have read, understood, and agreed to abide by this policy.}

\begin{tabular}{@{}p{4in}@{}}
\vskip0.3in
\hrule
\vskip3pt
Signature \& Date \\
\vskip0.3in
\hrule
\vskip3pt
Name \\
\vskip0.3in
\hrule
\vskip3pt
UCLA ID \\
\vskip0.3in
\hrule
\vskip3pt
Email address \\
\end{tabular}
\vskip1in


\end{document}
